Non-convergence in iterative imputation

### 2025-04-23 Manuscript/manuscript.qmd
plot results with CI

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(mice)
library(ggmice)
library(ggplot2)
library(dplyr)
load("../results/out.RData")
source("../R/evaluate_estimates.R")
performance <- evaluate_est(out) 
performance[performance$term == "b0", "term"] <- "Y"
performance <- mutate(performance,
  mech = factor(mech, levels = c("MCAR", "MAR"), ordered = TRUE),
  prop = factor(prop, levels = c(0.25, 0.5, 0.75), ordered = TRUE),
  term = factor(term, levels = c("Y", "X1", "X2", "X3"), ordered = TRUE))
results <- performance |> 
  group_by(method, mech, prop, .it, term) |> 
  summarise(across(c(bias, cov, ciw, ac_mean, psrf_mean, ac_sd, psrf_sd), \(x) mean(x, na.rm = TRUE))) 
```

```{r, echo=FALSE}
# # plot results per sim rep
# performance |>
#   filter(term == "X1", mech == "MAR", method == "MICE", prop == 0.75) |>
#   ggplot(aes(x = .it, y = bias)) + #, color = as.factor(prop)
#   geom_line(aes(group = .sim)) +
#   geom_smooth(method = "loess") +
#   # labs(
#   #   title = "Bias regression coefficient",
#   #   x = "Iteration number",
#   #   y = "Bias"
#   # ) +
#   theme_classic()
```

@@

```{r psrf_mean}
results |>
  filter(method == "MICE") |> 
  ggplot(aes(x = .it, y = psrf_mean, color = mech, linetype = mech)) +
  geom_hline(yintercept = 1, alpha = 0.1) + 
  geom_line() +
  facet_grid(term ~ prop) +
  theme_classic()
```

>>>>

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(mice)
library(ggmice)
library(ggplot2)
library(dplyr)
load("../results/out.RData")
source("../R/evaluate_estimates.R")
performance <- evaluate_est(out) 
performance[performance$term == "b0", "term"] <- "Y"
performance <- mutate(performance,
  mech = factor(mech, levels = c("MCAR", "MAR", "MNAR"), ordered = TRUE),
  prop = factor(prop, levels = c(0.25, 0.5, 0.75), ordered = TRUE),
  term = factor(term, levels = c("Y", "X1", "X2", "X3"), ordered = TRUE))
results <- performance |> 
  group_by(method, mech, prop, .it, term) |> 
  summarise(across(c(bias, cov, ciw, ac_mean, psrf_mean, ac_sd, psrf_sd), \(x) mean(x, na.rm = TRUE)))
results_ll <- performance |> 
  group_by(method, mech, prop, .it, term) |> 
  summarise(across(c(bias, cov, ciw, ac_mean, psrf_mean, ac_sd, psrf_sd), \(x) quantile(x, probs = c(0.025), na.rm = TRUE))) 
results_ul <- performance |> 
  group_by(method, mech, prop, .it, term) |> 
  summarise(across(c(bias, cov, ciw, ac_mean, psrf_mean, ac_sd, psrf_sd), \(x) quantile(x, probs = c(0.975), na.rm = TRUE))) 
results <- left_join(results, results_ll, by = c("method", "mech", "prop", ".it", "term"), suffix = c("", "_ll"))
results <- left_join(results, results_ul, by = c("method", "mech", "prop", ".it", "term"), suffix = c("", "_ul"))
```

```{r, echo=FALSE}
results |>
  filter(method == "MICE") |> 
  ggplot(aes(x = .it, y = psrf_mean)) +
  geom_hline(yintercept = 1, alpha = 0.1) + 
  geom_line() +
  geom_line(aes(y = psrf_mean_ll), linetype = "dashed") +
  geom_line(aes(y = psrf_mean_ul), linetype = "dashed") +
  facet_grid(term ~ prop + mech) +
  theme_classic()
```

@@

```{r psrf_mean}
results |>
  filter(method == "MICE") |> 
  ggplot(aes(x = .it, y = psrf_mean)) +
  geom_hline(yintercept = 1, alpha = 0.1) + 
  geom_line() +
  facet_grid(term ~ prop + mech) +
  theme_classic()
```
